Prospective testing for the prevalence or transience of a shock effect before it occurs

### 2021-11-16 prevalence_testing/postshocktest2021draft.tex
addition of manual and edits to manuscript

 Even if the data contain shock information for each donor, it is impossible to compute the adjusted conditional mean forecast based on $\mathcal{F}_{i, t-h}$ when $t -h \leq T_i^*$, i.e., we only have training data that do no have any shock information. Note that this is not a big problem when $t-h \geq T_i^* +1$ because  $\mathcal{F}_{i, t-h}$ starts to incorporate shock information. In the literature, \cite{lin2021minimizing} utilizes donor pool information to provide an unbiased estimator of the shock effect such that the adjusted  conditional mean forecast is the unadjusted one plus the shock effect estimate. However, the unbiased estimation comes with the cost of assuming certain models (in terms of first and second moments) for the shock effect across the donor pool and the method only works for additive shock effect model.  To our best knowledge, there  is no other available methods that can accommodate the case when the shock model is nonlinear. However, even if the model is misspecified, using additive shock effect model to approximate the scalar shock effect that occurs at $t=T_i^*+1$ may still help as opposed to doing nothing.

>>>>

 Even if the data contain shock information for each donor, it is impossible to compute the adjusted conditional mean forecast based on $\mathcal{F}_{i, t-h}$ when $t -h \leq T_i^*$, i.e., we only have training data that do no have any shock information. Note that this is not a big problem when $t-h \geq T_i^* +1$ because  $\mathcal{F}_{i, t-h}$ starts to incorporate shock information. In the literature, \cite{lin2021minimizing} utilizes donor pool information to provide an consistent estimator of the shock effect such that the adjusted  conditional mean forecast is the unadjusted one plus the shock effect estimate. However, the consistent estimation comes with the cost of assuming certain models (in terms of first and second moments) for the shock effect across the donor pool and the method only works for additive shock effect model.  To our best knowledge, there  is no other available methods that can accommodate the case when the shock model is nonlinear. However, even if the model is misspecified, using additive shock effect model to approximate the scalar shock effect that occurs at $t=T_i^*+1$ may still help as opposed to doing nothing.

 With the presence of autoregressive parameters in some models, unbiased estimation with OLS  is not feasible but the bias is $O(T^{-1})$, where $T$ is the time series length \citep{shaman1988bias}. In this paper, we use the OLS estimates to approximate the adjusted conditional mean forecast and unadjusted one. The bias decades away as $T\to \infty$.
